# Current Student Data Book By Subject {-}

<!-- {#current} -->

# Academic Program Reports – Fall 2018

## API Report by College and Academic Program: Fall 2018

## Teacher Education – API Report by College and Academic Program: Fall 2018



# Accountability

## 2018-19 University PMP Report

## 2018-19 University PMP Data Explorer (Tableau)

## 2017-18 University PMP Report

## 2016-17 University PMP Report

## 2015-16 Year-End University PMP Report – Final

## 2014-15 Year-End University PMP Report – Final

## 2013-14 Year-End University PMP Report – Final

## 2012-13 Year-End University PMP Report – Final

## 2011-12 Year-End University PMP Report – Final

## 2010-11 Year-End University PMP Report – Final

## 2009-10 Year-End University PMP Report – Final

## 2008-09 Year-End University PMP Report – Final



# Admissions (New Students) – Fall 2018

## Admissions to Undergraduate and Graduate Degree Programs by College

## Undergraduate Advanced Standing Transfers by Type of Sending College

## Admissions by Full-/Part-time Status and Gender

### ADMS_0003_Total New Undergraduate and Graduate Students by Full-time/Part-time Attendance, Gender and College

### ADMS_0004_First-time Freshmen by Full-time/Part-time Attendance, Gender and College

### ADMS_0005_Undergraduate Advanced Standing Transfers by Full-time/Part-time Attendance, Gender and College

### ADMS_0006_Total New Undergraduate Students by Full-time/Part-time Attendance, Gender and College

### ADMS_0007_Total New Graduate and First-professional Students by Full-time/Part-time Attendance, Gender and College

## Admissions by Degree Pursued

### ADMS_0008_First-time Freshmen by Degree Pursued, Full-time/Part-time Attendance, and College

### ADMS_0009_Undergraduate Advanced Standing Transfers by Degree Pursued, Full-time/Part-time Attendance, and College

### ADMS_0010_Total New Undergraduate Students by Degree Pursued, Full-time/Part-time Attendance, and College

### ADMS_0011_Total New Graduate and First-professional Students by Degree Pursued, Full-time/Part-time Attendance, and College



# Degrees Granted – 2018-2019

## Degrees Granted by Level
 
### DEGR_0001_Summary of Degrees Granted by College

### DEGR_0002_Certificate and Associate Degrees Granted by College

### DEGR_0003_Baccalaureate Degrees Granted by College

### DEGR_0004_Master’s Degrees Granted by College

### DEGR_0005_Advanced Certificates, Doctoral Degrees and First-professional Degrees Granted by College

## Degrees Granted by Race/Ethnicity

### DEGR_0006_Summary of Degrees Granted by Race/Ethnicity and Gender: Percentages

## Degrees Conferred – Trends

### DEGR_0007_Degrees Conferred at The City University of New York



# Enrollment – Fall 2018 - datatable

## Adult and Continuing Education (ACE, Non-Credit) Program Registration Trends

## Undergraduate and Graduate Enrollment

### ENRL_0001_Total Enrollment by Undergraduate and Graduate Level, Full-time/Part-time Attendance, and College

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
library(kableExtra)
library(DT)
library(magrittr)
library(stringr)
library(htmlTable)
```

```{r data}
# Import numerical data columns
data <- read.csv("S:/DicovererWorkbooks/Workbook2.csv", header=FALSE, stringsAsFactors = FALSE, skip = 5)

# Import headers
head1 <- c("", "", rep("Undergraduate",3), rep("Graduate",3), "")
head2 <- c("SenCom", "College", rep(c("Full-time", "Part-time", "Total"),2), "Total")

cols <- paste(head1, head2, sep = "<br/>", collapse = NULL)
cols[c(1, 2, 9)] = c("SenCom", "College", "Total")

# Set headers 
names(data) <- cols

# Make total rows uppercase
# data$SenCom <- toupper(data$SenCom)

# Combine first two columns
data$College <- ifelse(data$College == "", data$SenCom, data$College)
data <- data[-1]

# Calculate totals
data['Total<br/>Full-time'] <- rowSums(data[,c(2,5)], na.rm=TRUE)
data['Total<br/>Part-time'] <- rowSums(data[,c(3,6)], na.rm=TRUE)

# Reorder columns
data <- data[c(1:7,9,10,8)]

# Reorder rows
data <- data[c(2:19,1,21:27,20,28),]
row.names(data) <- NULL

# Rename Last row
data[c(19, 27, 28),1] <- c("SUBTOTAL SENIOR COLLEGES","SUBTOTAL COMMUNITY COLLEGES","TOTAL UNIVERSITY")

# ---------------------------------------------------------------------------- #
# Format numbers - DOES NOT WORK!!!
#data[2:10] <- format(data[2:10], big.mark   = ",")
#data[is.na.data.frame(data)] <- ""
# NONE OF THE ABOVE FORMATTING WORKS!  When done this way, can't stop NA from printing.
# ---------------------------------------------------------------------------- #

table_title <- "Total Enrollment by Undergraduate and Graduate Level, Full-time/Part-time Attendance, and College - Fall 2018"
```

```{r datatable, include=FALSE}
#'//////////////////////////////////////////////////////////////////////////////
#' FILE: datatable.R
#' AUTHOR: David Ruvolo
#' CREATED: 2019-12-05
#' MODIFIED: 2020-01-13
#' PURPOSE: build datatable function and helpers
#' STATUS: working
#' PACKAGES: htmltools
#' COMMENTS:
#'      The datatable function generates an html table from a dataset.
#'      This func returns a shiny tagList object which can be used in shiny
#'      applications, markdown documents, or written to an html file. The
#'      datatable function takes the following arguments.
#'
#'      ARGUMENTS:
#'      - data: the input dataset
#'      - id: an identifier for the table ideal for styling specific tables
#'            or for use in js
#'      - caption: a title for the table (recommended for accessible tables)
#'      - options:
#'          - responsive: a logical arg for turning on/off the rendering of
#'                      additional elements for responsive tables (i.e., span).
#'                      (Default = FALSE)
#'          - rowHeaders: a bool that renders the first cell of every row
#'              as a row header. This is useful for datasets where all data
#'              in a row is related, e.g., patient data. If set to TRUE,
#'              the data must be organized so that the row header is the
#'              first column.
#'
#'      ABOUT:
#'      The datatable function requires two helper functions: 1) to generate the
#'      table header and another used 2) to generate the table body. The func
#'      build_header() renders the <thead> element according to the input data.
#'      The build_body functions renders the table's <tbody> based on the input
#'      and the options. This function uses a nested lapplys to iterate each row
#'      and cell. If the responsive opt is TRUE, then the function will return
#'      a <span> element with the current cell's column name. <span> has
#'      the class `hidden-colname` that hides/shows the element based on screen
#'      size (see datatable.css). Role attributes are added in the event
#'      the display properties are altered in css.
#'//////////////////////////////////////////////////////////////////////////////

# ~ 1 ~
# DEFINE HELPER FUNCTIONS
datatable_helpers <- list()

# ~ a ~
# FUNCTION: build_header
datatable_helpers$build_header <- function(data, options) {
    columns <- colnames(data)
    cells <- lapply(1:length(columns), function(n) {

        # define cell content: as html or text
        if (isTRUE(options$asHTML)) {
            cell_value <- htmltools::HTML(columns[n])
        } else {
            cell_value <- columns[n]
        }

        # build header
        cell <- htmltools::tags$th(scope = "col", cell_value)
        cell
    })

    # return header
    htmltools::tags$thead(
        htmltools::tags$tr(role = "row", cells)
    )
}

# ~ b ~
# FUNCTION: build_body
datatable_helpers$build_body <- function(data, options) {
    body <- lapply(1:NROW(data), function(row) {
        cells <- lapply(1:NCOL(data), function(col) {

            # process options: render as html or escape?
            if (isTRUE(options$asHTML)) {
                cell_value <- htmltools::HTML(data[row, col])
            } else {
                cell_value <- data[row, col]
            }

            # process options$rowHeaders (this generates the cell)
            if (isTRUE(options$rowHeaders) && col == 1) {
                if (isTRUE(options$responsive)) {
                    cell <- htmltools::tags$th(role = "rowheader")
                    cell$children <- list(
                        htmltools::tags$span(
                            class = "hidden-colname",
                            `aria-hidden` = "true",
                            htmltools::HTML(colnames(data)[col])
                        ),
                        cell_value
                    )
                } else {
                    cell <- htmltools::tags$th(role = "rowheader", cell_value)
                }
            } else {
                cell <- htmltools::tags$td(role = "cell", datavalue=cell_value)
                # process options: responsive
                if (isTRUE(options$responsive)) {
                    cell$children <- list(
                        htmltools::tags$span(
                            class = "hidden-colname",
                            `aria-hidden` = "true",
                            htmltools::HTML(gsub("<br/>", " - ", colnames(data)[col]))
                        )
                    )
                } 
            }

            # return cell
            cell
        })
#################################################################################
##### Added 'totals = "yes"' to rows that contain the word total in the row header  
##### so that they can be styled by the css stylesheet...
        
        #print(grepl("total", as.character(cells[[1]]), ignore.case = TRUE))
        if (grepl("subtotal", as.character(cells[[1]]), ignore.case = TRUE)) {
            htmltools::tags$tr(role = "row", subtotals = "yes", cells)
        } else if (grepl("total", as.character(cells[[1]]), ignore.case = TRUE)) {
            htmltools::tags$tr(role = "row", totals = "yes", cells)
        } else {
            htmltools::tags$tr(role = "row", cells)
        }
        
        # return cells in a row
        #htmltools::tags$tr(role = "row", cells)
#################################################################################
    })
 
    # return body
    htmltools::tags$tbody(body)
}

#'////////////////////////////////////////

# ~ 2 ~
# FUNCTION: datatable
datatable <- function(data, id = NULL, caption = NULL, options = list(responsive = FALSE, rowHeaders = TRUE, asHTML = TRUE)) {

    # render table and table elements
    tbl <- htmltools::tags$table(class = "datatable",
        datatable_helpers$build_header(data, options),
        datatable_helpers$build_body(data, options)
    )

    # add id
    if (!is.null(id)) {
        tbl$attribs$id <- paste0("datatable-", id)
    }

    # should a caption be rendered?
    if (!is.null(caption)) {
        tbl$children <- list(
            htmltools::tags$caption(caption),
            tbl$children
        )
    }

    # return
    tbl
}
```

```{r}
# ---------------------------------------------------------------------------- #
# Format numbers and remove NA's
# data[is.na(data)] <- NULL
data3 <- data
data3[2:10] <- format(data3[2:10], big.mark   = ",")
data3$`Undergraduate<br/>Full-time` <- str_replace_all(data3$`Undergraduate<br/>Full-time`, ".+NA", "0")
data3$`Undergraduate<br/>Part-time` <- str_replace_all(data3$`Undergraduate<br/>Part-time`, ".+NA", "0")
data3$`Undergraduate<br/>Total` <- str_replace_all(data3$`Undergraduate<br/>Total`, ".+NA", "0")
data3$`Graduate<br/>Full-time` <- str_replace_all(data3$`Graduate<br/>Full-time`, ".+NA", "0")
data3$`Graduate<br/>Part-time` <- str_replace_all(data3$`Graduate<br/>Part-time`, ".+NA", "0")
data3$`Graduate<br/>Total` <- str_replace_all(data3$`Graduate<br/>Total`, ".+NA", "0")
data3$`Total<br/>Full-time` <- str_replace_all(data3$`Total<br/>Full-time`, ".+NA", "0")
data3$`Total<br/>Part-time` <- str_replace_all(data3$`Total<br/>Part-time`, ".+NA", "0")
data3$Total <- str_replace_all(data3$Total, ".+NA", "0")
# THIS IS REALLY NASTY BUT IT WORKS!
# ---------------------------------------------------------------------------- #
```

###### Accessibility Instructions: This table contains `r table_title`.  Footnotes display immediately below the table. 

```{r output}
t <- datatable(data3, id="Enrollment Test", caption = table_title, 
               options = list(responsive = TRUE, rowHeaders = TRUE, asHTML = TRUE))
#writeLines(as.character(t), "S:/R/Enrollment_datatable.html")
#cat(as.character(t))
t
```

##### Note: Enrollment for Guttman, Kingsborough, and LaGuardia are preliminary; final enrollment will be available in March.


### ENRL_0002_Undergraduate Enrollment by Degree/Non-degree Status, Full-time/Part-time Attendance, and College

### ENRL_0003_Graduate and First-professional Enrollment by Degree/Non-degree Status, Full-time/Part-time Attendance, and College

### ENRL_0004_Total Enrollment by Undergraduate and Graduate Level, Degree/Nondegree Status, and College

### ENRL_0005_Total Enrollment by Undergraduate and Graduate Level, Gender and College

### ENRL_0006_Full-Time Equivalent (FTE) Student Enrollment by Undergraduate and Graduate Level, and College

## Enrollment by Degree Pursued

### ENRL_0007_Total Enrollment by Undergraduate and Graduate Level, Degree Pursued and College

## Enrollment by Residency and Age

### ENRL_0045_Total Enrollment by Residency and College

### ENRL_0046_Undergraduate Enrollment by Age and College

## Five-year Trends in Total Enrollment

### ENRL_0008_Five-year Trends in Total Fall Enrollment – Total University

### ENRL_0009_Five-year Trends in Total Fall Enrollment – Senior and Comprehensive Colleges

### ENRL_0010_Five-year Trends in Total Fall Enrollment – Community Colleges

## Five-year Trends in Total Fall Enrollment, by College

### Senior Colleges

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Baruch College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Brooklyn College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – City College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Hunter College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – John Jay College of Criminal Justice

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Lehman College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Medgar Evers College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – New York City College of Technology

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Queens College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – College of Staten Island

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – York College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Graduate School and University Center

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – School of Journalism

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – School of Professional Studies

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Labor & Urban Studies

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Public Health

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Law School

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Medical School

### Community Colleges
 
#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Borough of Manhattan Community College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Bronx Community College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Guttman Community College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Hostos Community College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Kingsborough Community College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – LaGuardia Community College

#### ENRL_0011_Five-year Trends in Total Fall Enrollment – Queensborough Community College

## Long-term Trends in Total Fall Enrollment

### ENRL_0012_Long-term Trends in Fall Enrollment: Total University

### ENRL_0013_Long-term Trends in Fall Enrollment: First-time Freshmen

### ENRL_0014_Long-term Trends in Fall Enrollment: Transfers



# Enrollment – Fall 2018 - other options

## kableExtra with advanced styling

##### `r table_title`

```{r kableExtra_advanced_2, results='asis'}

data2 <- data
names(data2) <- c("College", rep(c("Full-time", "Part-time", "Total"), 3))

data2 %>%
  kable(format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, font_size = "0.75em") %>%
  add_header_above(c(" " = 1, "Undergraduate" = 3, "Graduate" = 3, "Total" = 3),
                   extra_css = "border-bottom: 1px solid",
                   background = "#ebf1fd", 
                   bold = TRUE) %>%
  row_spec(c(0), bold = TRUE, background = "#ebf1fd", 
           extra_css = "border-bottom: 1px solid") %>%
  row_spec(c(19,27, 28), bold = TRUE, background = "#ebf1fd") %>%
  column_spec(1, bold = TRUE, width_min = "10em") %>%
  column_spec(2:10, width_min = "5em")
```

## kableExtra with advanced styling part 2

##### `r table_title`

```{r kableExtra_advanced, results='asis'}

data2 %>%
  kable(format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, font_size = "0.75em") %>%
  add_header_above(c(" " = 1, "Undergraduate" = 3, "Graduate" = 3, "Total" = 3), 
                   color = "white", 
                   background = "#465e8c", 
                   bold = TRUE) %>%
  row_spec(c(0,28), color = "white", background = "#465e8c") %>%
  row_spec(c(19,27), color = "white", background = "#787878") %>%
  column_spec(1, bold = TRUE, width_min = "10em") %>%
  column_spec(2:10, width_min = "5em")
```

## DT

```{r DT, results='asis'}
data %>%
  DT::datatable(caption = table_title, 
            class = 'stripe hover compact table-condensed', 
            rownames = FALSE,
            filter = 'top',
            extensions = 'Buttons', 
            options = list(dom = 'Bfrtip', 
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           pageLength = 50)
            #style = 'default'
            ) %>%
  formatCurrency(c(2:10),currency = "", interval = 3, mark = ",", digits = 0)
```

## DT with double header

**No Bootstrap theme is used here.**

**Double header doesn't download properly with the excel, pdf etc... buttons.**

**Problem is that the reason that these columns are formatted so nicely and evenly-spaced is because the header labels are shorter and so the columns do not have to be expanded to fit the text.  If we want shorter header names we may have to make more tables with less columns.**

**There's also no way that I have found so far to format the total rows to be a different color to separate them out from the colleges, so we may want to remove the total and subtotal rows.**

```{r DT_styled, results='asis'}

# a custom table container
double_header = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, 'College'),
      th(colspan = 3, 'Undergraduate'),
      th(colspan = 3, 'Graduate'),
      th(colspan = 3, 'Total')
    ),
    tr(
      lapply(rep(c("Full-time", "Part-time", "Total"), 3), th)
    )
  )
))

data %>%
  DT::datatable(container = double_header, 
            caption = table_title,  
            class = 'stripe hover compact nowrap table-condensed',
            rownames = FALSE,
            filter = 'top',
            extensions = 'Buttons', 
            options = list(dom = 'Bfrtip', 
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           pageLength = 50)
            ) %>%
  formatCurrency(c(2:10),currency = "", interval = 3, mark = ",", digits = 0)
```

## htmlTable

```{r}
htmlTable(data, rnames=FALSE, #total=TRUE,
          #col.rgroup = c("none", "#F7F7F7"),
          col.columns = c("none", rep(c("none", "none", "#F5FBFF"), 3)),
          total = "tspanner",
          css.total = rep("border-top: 1px solid grey; font-weight: 900; background: #F7F7F7", 3),
          tspanner = c("Senior Colleges", "Community Colleges", "Grand Total"),
          n.tspanner = c(19, 8, 1))
```


# Race/Ethnicity – Fall 2018




# Retention & Graduation – Fall 2018




# SEEK/College Discovery – Fall 2018




# STEM Enrollment & Degrees Granted – Fall 2017/2016-2017




# Student Profile / Demographic Information – Fall 2016



