# <strong>Current Student Data Book By Subject</strong> {-}

<!-- {#current} -->

# Academic Program Reports – Fall 2018

## API Report by College and Academic Program: Fall 2018

## Teacher Education – API Report by College and Academic Program: Fall 2018



# Accountability

## 2018-19 University PMP Report

## 2018-19 University PMP Data Explorer (Tableau)

## 2017-18 University PMP Report

## 2016-17 University PMP Report

## 2015-16 Year-End University PMP Report – Final

## 2014-15 Year-End University PMP Report – Final

## 2013-14 Year-End University PMP Report – Final

## 2012-13 Year-End University PMP Report – Final

## 2011-12 Year-End University PMP Report – Final

## 2010-11 Year-End University PMP Report – Final

## 2009-10 Year-End University PMP Report – Final

## 2008-09 Year-End University PMP Report – Final



# Admissions (New Students) – Fall 2018

## Admissions to Undergraduate and Graduate Degree Programs by College

## Undergraduate Advanced Standing Transfers by Type of Sending College

## Admissions by Full-/Part-time Status and Gender

### Total New Undergraduate and Graduate Students by Full-time/Part-time Attendance, Gender and College

### First-time Freshmen by Full-time/Part-time Attendance, Gender and College

### Undergraduate Advanced Standing Transfers by Full-time/Part-time Attendance, Gender and College

### Total New Undergraduate Students by Full-time/Part-time Attendance, Gender and College

### Total New Graduate and First-professional Students by Full-time/Part-time Attendance, Gender and College

## Admissions by Degree Pursued

### First-time Freshmen by Degree Pursued, Full-time/Part-time Attendance, and College

### Undergraduate Advanced Standing Transfers by Degree Pursued, Full-time/Part-time Attendance, and College

### Total New Undergraduate Students by Degree Pursued, Full-time/Part-time Attendance, and College

### Total New Graduate and First-professional Students by Degree Pursued, Full-time/Part-time Attendance, and College



# Degrees Granted – 2018-2019

## Degrees Granted by Level
 
### Summary of Degrees Granted by College

### Certificate and Associate Degrees Granted by College

### Baccalaureate Degrees Granted by College

### Master’s Degrees Granted by College

### Advanced Certificates, Doctoral Degrees and First-professional Degrees Granted by College

## Degrees Granted by Race/Ethnicity

### Summary of Degrees Granted by Race/Ethnicity and Gender: Percentages

## Degrees Conferred – Trends

### Degrees Conferred at The City University of New York



# Enrollment – Fall 2018 - datatable

## Adult and Continuing Education (ACE, Non-Credit) Program Registration Trends

## Undergraduate and Graduate Enrollment

### Total Enrollment by Undergraduate and Graduate Level, Full-time/Part-time Attendance, and College {-}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
library(kableExtra)
library(DT)
library(magrittr)
library(stringr)
library(htmlTable)
library(webshot)
```

```{r data}
# Import numerical data columns
data <- read.csv("S:/DicovererWorkbooks/Workbook2.csv", header=FALSE, stringsAsFactors = FALSE, skip = 5)

# Import headers
head1 <- c("", "", rep("Undergraduate",3), rep("Graduate",3), "")
head2 <- c("SenCom", "College", rep(c("Full-time", "Part-time", "Total"),2), "Total")

cols <- paste(head1, head2, sep = "<br/>", collapse = NULL)
cols[c(1, 2, 9)] = c("SenCom", "College", "Total")

# Set headers 
names(data) <- cols

# Make total rows uppercase
# data$SenCom <- toupper(data$SenCom)

# Combine first two columns
data$College <- ifelse(data$College == "", data$SenCom, data$College)
data <- data[-1]

# Calculate totals
data['Total<br/>Full-time'] <- rowSums(data[,c(2,5)], na.rm=TRUE)
data['Total<br/>Part-time'] <- rowSums(data[,c(3,6)], na.rm=TRUE)

# Reorder columns
data <- data[c(1:7,9,10,8)]

# Reorder rows
data <- data[c(2:19,1,21:27,20,28),]
row.names(data) <- NULL

# Rename Last row
data[c(19, 27, 28),1] <- c("SUBTOTAL SENIOR COLLEGES","SUBTOTAL COMMUNITY COLLEGES","TOTAL UNIVERSITY")

# ---------------------------------------------------------------------------- #
# Format numbers - DOES NOT WORK!!!
#data[2:10] <- format(data[2:10], big.mark   = ",")
#data[is.na.data.frame(data)] <- ""
# NONE OF THE ABOVE FORMATTING WORKS!  When done this way, can't stop NA from printing.
# ---------------------------------------------------------------------------- #

table_title <- "Total Enrollment by Undergraduate and Graduate Level, Full-time/Part-time Attendance, and College - Fall 2018"
```

```{r datatable, include=FALSE}
#'//////////////////////////////////////////////////////////////////////////////
#' FILE: datatable.R
#' AUTHOR: David Ruvolo
#' CREATED: 2019-12-05
#' MODIFIED: 2020-01-13
#' PURPOSE: build datatable function and helpers
#' STATUS: working
#' PACKAGES: htmltools
#' COMMENTS:
#'      The datatable function generates an html table from a dataset.
#'      This func returns a shiny tagList object which can be used in shiny
#'      applications, markdown documents, or written to an html file. The
#'      datatable function takes the following arguments.
#'
#'      ARGUMENTS:
#'      - data: the input dataset
#'      - id: an identifier for the table ideal for styling specific tables
#'            or for use in js
#'      - caption: a title for the table (recommended for accessible tables)
#'      - options:
#'          - responsive: a logical arg for turning on/off the rendering of
#'                      additional elements for responsive tables (i.e., span).
#'                      (Default = FALSE)
#'          - rowHeaders: a bool that renders the first cell of every row
#'              as a row header. This is useful for datasets where all data
#'              in a row is related, e.g., patient data. If set to TRUE,
#'              the data must be organized so that the row header is the
#'              first column.
#'
#'      ABOUT:
#'      The datatable function requires two helper functions: 1) to generate the
#'      table header and another used 2) to generate the table body. The func
#'      build_header() renders the <thead> element according to the input data.
#'      The build_body functions renders the table's <tbody> based on the input
#'      and the options. This function uses a nested lapplys to iterate each row
#'      and cell. If the responsive opt is TRUE, then the function will return
#'      a <span> element with the current cell's column name. <span> has
#'      the class `hidden-colname` that hides/shows the element based on screen
#'      size (see datatable.css). Role attributes are added in the event
#'      the display properties are altered in css.
#'//////////////////////////////////////////////////////////////////////////////

# ~ 1 ~
# DEFINE HELPER FUNCTIONS
datatable_helpers <- list()

# ~ a ~
# FUNCTION: build_header
datatable_helpers$build_header <- function(data, options) {
    columns <- colnames(data)
    cells <- lapply(1:length(columns), function(n) {

        # define cell content: as html or text
        if (isTRUE(options$asHTML)) {
            cell_value <- htmltools::HTML(columns[n])
        } else {
            cell_value <- columns[n]
        }

        # build header
        cell <- htmltools::tags$th(scope = "col", cell_value)
        cell
    })

    # return header
    htmltools::tags$thead(
        htmltools::tags$tr(role = "row", cells)
    )
}

# ~ b ~
# FUNCTION: build_body
datatable_helpers$build_body <- function(data, options) {
    body <- lapply(1:NROW(data), function(row) {
        cells <- lapply(1:NCOL(data), function(col) {

            # process options: render as html or escape?
            if (isTRUE(options$asHTML)) {
                cell_value <- htmltools::HTML(data[row, col])
            } else {
                cell_value <- data[row, col]
            }

            # process options$rowHeaders (this generates the cell)
            if (isTRUE(options$rowHeaders) && col == 1) {
                if (isTRUE(options$responsive)) {
                    cell <- htmltools::tags$th(role = "rowheader")
                    cell$children <- list(
                        htmltools::tags$span(
                            class = "hidden-colname",
                            `aria-hidden` = "true",
                            htmltools::HTML(colnames(data)[col])
                        ),
                        cell_value
                    )
                } else {
                    cell <- htmltools::tags$th(role = "rowheader", cell_value)
                }
            } else {
                cell <- htmltools::tags$td(role = "cell", datavalue=cell_value)
                # process options: responsive
                if (isTRUE(options$responsive)) {
                    cell$children <- list(
                        htmltools::tags$span(
                            class = "hidden-colname",
                            `aria-hidden` = "true",
                            htmltools::HTML(gsub("<br/>", " - ", colnames(data)[col]))
                        )
                    )
                } 
            }

            # return cell
            cell
        })
#################################################################################
##### Added 'totals = "yes"' to rows that contain the word total in the row header  
##### so that they can be styled by the css stylesheet...
        
        #print(grepl("total", as.character(cells[[1]]), ignore.case = TRUE))
        if (grepl("subtotal", as.character(cells[[1]]), ignore.case = TRUE)) {
            htmltools::tags$tr(role = "row", subtotals = "yes", cells)
        } else if (grepl("total", as.character(cells[[1]]), ignore.case = TRUE)) {
            htmltools::tags$tr(role = "row", totals = "yes", cells)
        } else {
            htmltools::tags$tr(role = "row", cells)
        }
        
        # return cells in a row
        #htmltools::tags$tr(role = "row", cells)
#################################################################################
    })
 
    # return body
    htmltools::tags$tbody(body)
}

#'////////////////////////////////////////

# ~ 2 ~
# FUNCTION: datatable
datatable <- function(data, id = NULL, caption = NULL, options = list(responsive = FALSE, rowHeaders = TRUE, asHTML = TRUE)) {

    # render table and table elements
    tbl <- htmltools::tags$table(class = "datatable",
        datatable_helpers$build_header(data, options),
        datatable_helpers$build_body(data, options)
    )

    # add id
    if (!is.null(id)) {
        tbl$attribs$id <- paste0("datatable-", id)
    }

    # should a caption be rendered?
    if (!is.null(caption)) {
        tbl$children <- list(
            htmltools::tags$caption(caption),
            tbl$children
        )
    }

    # return
    tbl
}
```

```{r}
# ---------------------------------------------------------------------------- #
# Format numbers and remove NA's
# data[is.na(data)] <- NULL
data3 <- data
data3[2:10] <- format(data3[2:10], big.mark   = ",")
data3$`Undergraduate<br/>Full-time` <- str_replace_all(data3$`Undergraduate<br/>Full-time`, ".+NA", "0")
data3$`Undergraduate<br/>Part-time` <- str_replace_all(data3$`Undergraduate<br/>Part-time`, ".+NA", "0")
data3$`Undergraduate<br/>Total` <- str_replace_all(data3$`Undergraduate<br/>Total`, ".+NA", "0")
data3$`Graduate<br/>Full-time` <- str_replace_all(data3$`Graduate<br/>Full-time`, ".+NA", "0")
data3$`Graduate<br/>Part-time` <- str_replace_all(data3$`Graduate<br/>Part-time`, ".+NA", "0")
data3$`Graduate<br/>Total` <- str_replace_all(data3$`Graduate<br/>Total`, ".+NA", "0")
data3$`Total<br/>Full-time` <- str_replace_all(data3$`Total<br/>Full-time`, ".+NA", "0")
data3$`Total<br/>Part-time` <- str_replace_all(data3$`Total<br/>Part-time`, ".+NA", "0")
data3$Total <- str_replace_all(data3$Total, ".+NA", "0")
# THIS IS REALLY NASTY BUT IT WORKS!
# ---------------------------------------------------------------------------- #
```

<p class="accessibility_instructions">Accessibility Instructions: This table contains `r table_title`.  Footnotes display immediately below the table.</p>

```{r output}
t <- datatable(data3, id="Enrollment Test", caption = NULL, 
               options = list(responsive = TRUE, rowHeaders = TRUE, asHTML = TRUE))
#writeLines(as.character(t), "S:/R/Enrollment_datatable.html")
#cat(as.character(t))
t
```

Note: Enrollment for Guttman, Kingsborough, and LaGuardia are preliminary; final enrollment will be available in March.


### Undergraduate Enrollment by Degree/Non-degree Status, Full-time/Part-time Attendance, and College {-}

### Graduate and First-professional Enrollment by Degree/Non-degree Status, Full-time/Part-time Attendance, and College {-}

### Total Enrollment by Undergraduate and Graduate Level, Degree/Nondegree Status, and College {-}

### Total Enrollment by Undergraduate and Graduate Level, Gender and College {-}

### Full-Time Equivalent (FTE) Student Enrollment by Undergraduate and Graduate Level, and College {-}

## Enrollment by Degree Pursued

### Total Enrollment by Undergraduate and Graduate Level, Degree Pursued and College {-}

## Enrollment by Residency and Age

### Total Enrollment by Residency and College {-}

### Undergraduate Enrollment by Age and College {-}

## Five-year Trends in Total Enrollment

### Five-year Trends in Total Fall Enrollment – Total University {-}

### Five-year Trends in Total Fall Enrollment – Senior and Comprehensive Colleges {-}

### Five-year Trends in Total Fall Enrollment – Community Colleges {-}

## Five-year Trends in Total Fall Enrollment, by College

### Senior Colleges

#### Five-year Trends in Total Fall Enrollment – Baruch College {-}

#### Five-year Trends in Total Fall Enrollment – Brooklyn College {-}

#### Five-year Trends in Total Fall Enrollment – City College {-}

#### Five-year Trends in Total Fall Enrollment – Hunter College {-}

#### Five-year Trends in Total Fall Enrollment – John Jay College of Criminal Justice {-}

#### Five-year Trends in Total Fall Enrollment – Lehman College {-}

#### Five-year Trends in Total Fall Enrollment – Medgar Evers College {-}

#### Five-year Trends in Total Fall Enrollment – New York City College of Technology {-}

#### Five-year Trends in Total Fall Enrollment – Queens College {-}

#### Five-year Trends in Total Fall Enrollment – College of Staten Island {-}

#### Five-year Trends in Total Fall Enrollment – York College {-}

#### Five-year Trends in Total Fall Enrollment – Graduate School and University Center {-}

#### Five-year Trends in Total Fall Enrollment – School of Journalism {-}

#### Five-year Trends in Total Fall Enrollment – School of Professional Studies {-}

#### Five-year Trends in Total Fall Enrollment – Labor & Urban Studies {-}

#### Five-year Trends in Total Fall Enrollment – Public Health {-}

#### Five-year Trends in Total Fall Enrollment – Law School {-}

#### Five-year Trends in Total Fall Enrollment – Medical School {-}

### Community Colleges
 
#### Five-year Trends in Total Fall Enrollment – Borough of Manhattan Community College {-}

#### Five-year Trends in Total Fall Enrollment – Bronx Community College {-}

#### Five-year Trends in Total Fall Enrollment – Guttman Community College {-}

#### Five-year Trends in Total Fall Enrollment – Hostos Community College {-}

#### Five-year Trends in Total Fall Enrollment – Kingsborough Community College {-}

#### Five-year Trends in Total Fall Enrollment – LaGuardia Community College {-}

#### Five-year Trends in Total Fall Enrollment – Queensborough Community College {-}

## Long-term Trends in Total Fall Enrollment

### Long-term Trends in Fall Enrollment: Total University {-}

### Long-term Trends in Fall Enrollment: First-time Freshmen {-}

### Long-term Trends in Fall Enrollment: Transfers {-}



# Enrollment – Fall 2018 - other options

## kableExtra with advanced styling

##### `r table_title` {-}

```{r kableExtra_advanced_2, results='asis'}

data2 <- data
names(data2) <- c("College", rep(c("Full-time", "Part-time", "Total"), 3))

data2 %>%
  kable(format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, font_size = "0.75em") %>%
  add_header_above(c(" " = 1, "Undergraduate" = 3, "Graduate" = 3, "Total" = 3),
                   extra_css = "border-bottom: 1px solid",
                   background = "#ebf1fd", 
                   bold = TRUE) %>%
  row_spec(c(0), bold = TRUE, background = "#ebf1fd", 
           extra_css = "border-bottom: 1px solid") %>%
  row_spec(c(19,27, 28), bold = TRUE, background = "#ebf1fd") %>%
  column_spec(1, bold = TRUE, width_min = "10em") %>%
  column_spec(2:10, width_min = "5em")
```

## kableExtra with advanced styling part 2

##### `r table_title` {-}

```{r kableExtra_advanced, results='asis'}

data2 %>%
  kable(format.args = list(big.mark = ",")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, font_size = "0.75em") %>%
  add_header_above(c(" " = 1, "Undergraduate" = 3, "Graduate" = 3, "Total" = 3), 
                   color = "white", 
                   background = "#465e8c", 
                   bold = TRUE) %>%
  row_spec(c(0,28), color = "white", background = "#465e8c") %>%
  row_spec(c(19,27), color = "white", background = "#787878") %>%
  column_spec(1, bold = TRUE, width_min = "10em") %>%
  column_spec(2:10, width_min = "5em")
```

## DT

```{r DT, results='asis'}
data %>%
  DT::datatable(caption = table_title, 
            class = 'stripe hover compact table-condensed', 
            rownames = FALSE,
            filter = 'top',
            extensions = 'Buttons', 
            options = list(dom = 'Bfrtip', 
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           pageLength = 50)
            #style = 'default'
            ) %>%
  formatCurrency(c(2:10),currency = "", interval = 3, mark = ",", digits = 0)
```

## DT with double header

**No Bootstrap theme is used here.**

**Double header doesn't download properly with the excel, pdf etc... buttons.**

**Problem is that the reason that these columns are formatted so nicely and evenly-spaced is because the header labels are shorter and so the columns do not have to be expanded to fit the text.  If we want shorter header names we may have to make more tables with less columns.**

**There's also no way that I have found so far to format the total rows to be a different color to separate them out from the colleges, so we may want to remove the total and subtotal rows.**

```{r DT_styled, results='asis'}

# a custom table container
double_header = htmltools::withTags(table(
  class = 'display',
  thead(
    tr(
      th(rowspan = 2, 'College'),
      th(colspan = 3, 'Undergraduate'),
      th(colspan = 3, 'Graduate'),
      th(colspan = 3, 'Total')
    ),
    tr(
      lapply(rep(c("Full-time", "Part-time", "Total"), 3), th)
    )
  )
))

data %>%
  DT::datatable(container = double_header, 
            caption = table_title,  
            class = 'stripe hover compact nowrap table-condensed',
            rownames = FALSE,
            filter = 'top',
            extensions = 'Buttons', 
            options = list(dom = 'Bfrtip', 
                           buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                           pageLength = 50)
            ) %>%
  formatCurrency(c(2:10),currency = "", interval = 3, mark = ",", digits = 0)
```

## htmlTable

### `r table_title` {-}

```{r}
htmlTable(data, rnames=FALSE, #total=TRUE,
          #col.rgroup = c("none", "#F7F7F7"),
          col.columns = c("none", rep(c("none", "none", "#F5FBFF"), 3)),
          total = "tspanner",
          css.total = rep("border-top: 1px solid grey; font-weight: 900; background: #F7F7F7", 3),
          tspanner = c("Senior Colleges", "Community Colleges", "Grand Total"),
          n.tspanner = c(19, 8, 1))
```


# Race/Ethnicity – Fall 2018

### Summary of Degrees Granted by Race/Ethnicity and Gender: Percentages {-}

## Enrollment by Race/Ethnicity

### Total Enrollment by Race/Ethnicity and College: Percentages {-}

### Total Enrollment by Undergraduate and Graduate Level, Race/Ethnicity and College: Percentages {-}

### Total Enrollment by Race/Ethnicity, Gender and College {-}

### Total Enrollment by Race/Ethnicity, Gender and College (Percentages) {-}

### Undergraduate Enrollment by Race/Ethnicity, Gender, and College {-}

### Undergraduate Enrollment by Race and Gender (Percentages) {-}

### Graduate Enrollment by Race/Ethnicity and Gender {-}

### Graduate Enrollment by Race/Ethnicity and Gender (Percentages) {-}

## Racial/Ethnic Composition of New Students

### First-time Freshmen Enrollment by Race/Ethnicity and College: Percentages {-}

### Advanced Standing Transfer Enrollment by Race/Ethnicity and College: Percentages {-}


# Retention & Graduation – Fall 2018

<h2>**System Retention and Graduation Rates**</h2>

**System Retention Rates** are calculated as the percentage who are still enrolled at any CUNY college in the subsequent fall term(s) and have not yet earned a degree. **System Graduation Rates** are calculated as the percentage earning a degree at any CUNY college any time prior to the start of the subsequent fall term(s). Students earning a degree, even if lower than that originally pursued, are counted for that degree and not as still enrolled, even if they are still enrolled in the subsequent fall term. Students who have earned both an associate and a baccalaureate degree within a given time period are counted for the baccalaureate degree only.

## Ten-Year Retention and Graduation Rates of Entering Students – Associate Entrants - Total University

#### System Retention and Graduation Rates of Full-time First-time Freshmen in Associate Programs by Year of Entry: Total University {-}

#### System Retention and Graduation Rates of Full-time Transfers in Associate Programs by Year of Entry: Total University {-}

## System Retention and Grad Rates of All Full-time, First-time Freshmen in Associate Programs by Year of Entry: Colleges

### Comprehensive Colleges

#### John Jay College of Criminal Justice {-}

#### Medgar Evers College {-}

#### New York City College of Technology {-}

#### College of Staten Island {-}

### Community Colleges

#### Borough of Manhattan Community College {-}

#### Guttman Community College {-}

#### Bronx Community College {-}

#### Hostos Community College {-}

#### Kingsborough Community College {-}

#### LaGuardia Community College {-}

#### Queensborough Community College {-}

## Ten-Year Retention and Graduation Rates of Entering Students – Baccalaureate Entrants - Total University

#### System Retention and Graduation Rates of Full-time First-time Freshmen in Baccalaureate Programs by Year of Entry:* Total University {-}

#### System Retention and Graduation Rates of Full-time Transfers in Baccalaureate Programs by Year of Entry:* Total University {-}

## System Retention and Grad Rates of All Full-time, First-time Freshmen in Baccalaureate Programs by Year of Entry: Colleges

### Comprehensive Colleges

#### John Jay College of Criminal Justice {-}

#### Medgar Evers College {-}

#### New York City College of Technology {-}

#### College of Staten Island College {-}

### Senior Colleges

#### Baruch College {-}

#### Brooklyn College {-}

#### City College {-}

#### Hunter College {-}

#### Lehman College {-}

#### Queens College {-}

#### York College {-}


# SEEK and CD – Fall 2018

<h2>**Search for Education, Elevation, and Knowledge** and **College Discovery**</h2>

**SEEK (Search for Education, Elevation, and Knowledge)** and **CD (College Discovery)** are the two City University higher education opportunity programs, designed to assist high potential, low income students who otherwise might not be able to pursue a college degree because they are not academically well prepared for college level work. Since the late sixties, SEEK and CD have graduated thousands of highly motivated and talented students. Found on each of the seventeen undergraduate campuses, SEEK and CD offer an array of counseling and academic support initiatives to students who meet the University and New York State guidelines for Program admission.

## Enrollment by Race/Ethnicity

### Total SEEK/CD Enrollment by Race/Ethnicity, Gender and College {-}

### Total SEEK/CD Enrollment by Race/Ethnicity, Gender and College: Percentages {-}

## Long-term Trends in Total Enrollment

### Trends in SEEK/CD Enrollment {-}

### Trends in SEEK/CD First-time Freshmen Enrollment {-}

### Trends in SEEK/CD Enrollment in Associate Programs {-}

### Trends in SEEK/CD Enrollment in Baccalaureate Programs {-}

### Trends in SEEK/CD First-time Freshmen Enrollment in Associate Programs {-}

### Trends in SEEK/CD First-time Freshmen Enrollment in Baccalaureate Programs {-}

## Institution Retention and Graduation Rates

### Institution Retention and Graduation Rates of Special Program, Full-time First-time Freshmen in Associate Programs by Year of Entry: Total University {-}

### Institution Retention and Graduation Rates of Special Program, Full-time First-time Freshmen in Baccalaureate Programs by Year of Entry: Total University {-}

## System Retention and Graduation Rates

### System Retention and Graduation Rates of Special Program, Full-time First-time Freshmen in Associate Programs by Year of Entry: Total University {-}

### System Retention and Graduation Rates of Special Program, Full-time First-time Freshmen in Baccalaureate Programs by Year of Entry: Total University {-}


# STEM Enrollment & Degrees Granted – Fall 2017/2016-2017

## Enrollment

### Trends

#### Ten-Year Trends in Enrollment in Science, Technology, Engineering, and Math (STEM) Disciplines {-}

### by College

#### Enrollment in Science, Technology, Engineering, and Math (STEM) Disciplines by College: Fall 2017 {-}

### by Degree Pursued

#### Enrollment in Science, Technology, Engineering, and Math (STEM) Disciplines by Degree Pursued: Fall 2017 {-}

### by Race/Ethnicity

#### Enrollment in Science, Technology, Engineering, and Math (STEM) Disciplines by Race/Ethnicity: Fall 2017 {-}

#### Enrollment in Science, Technology, Engineering, and Math (STEM) Disciplines by Major and Race/Ethnicity: Fall 2017 {-}

### by Gender

#### Enrollment in Science, Technology, Engineering, and Math (STEM) Disciplines by Gender: Fall 2017 {-}

#### Enrollment in Science, Technology, Engineering, and Math (STEM) Disciplines by Major and Gender: Fall 2017 {-}

#### Enrollment in Science, Technology, Engineering, and Math (STEM) Disciplines by Gender and Race/Ethnicity: Fall 2017 {-}

## Degrees Granted

### Trends

#### Ten-Year Trends in Degrees Granted in Science, Technology, Engineering, and Math (STEM) Disciplines {-}

#### Ten-Year Trends in Baccalaureate Degrees Granted in Science, Technology, Engineering, and Math (STEM) Disciplines {-}

#### Ten-Year Trends in Associate Degrees Granted in Science, Technology, Engineering, and Math (STEM) Disciplines {-}

### by College

#### Degrees Granted in Science, Technology, Engineering, and Math (STEM) Disciplines, by College: 2016-2017 {-}

### by Degree Pursued

#### Degrees Granted in Science, Technology, Engineering, and Math (STEM) Disciplines by Degree: 2016-2017 {-}

### by Race/Ethnicity

#### Degrees Granted in Science, Technology, Engineering, and Math (STEM) Disciplines by Race/Ethnicity: 2016-2017 {-}

#### Degrees Granted in Science, Technology, Engineering, and Math (STEM) Disciplines by Major and Race/Ethnicity: 2016-2017 {-}

### by Gender

#### Degrees Granted in Science, Technology, Engineering, and Math (STEM) Disciplines by Gender: 2016-2017 {-}

#### Degrees Granted in Science, Technology, Engineering, and Math (STEM) Disciplines by Major and Gender: 2016-2017 {-}

#### Degrees Granted in Science, Technology, Engineering, and Math (STEM) Disciplines by Gender and Race/Ethnicity: 2016-2017 {-}


# Student Profile / Demographic Information – Fall 2016

## Fall 2018 Profile of CUNY Undergraduates 

## Country of Birth of Foreign Born Undergraduates: Fall 2017

## Ancestry of Undergraduates: Fall 2017

